Injrury Outcomes - WHW matrices

### 2021-11-29 injury_tables.Rmd
Regen injuries to get distances

>>>>

### True distances in a single file
```{r }
true_distances <- list()
for (city in cities) { # Loop for each city
  true_distances[[city]] <- io[[city]]$true_dist %>% 
    pivot_longer(!stage_mode, names_to = "scenario", values_to = "distance") %>% 
    mutate(city = city)
}
true_distances_df <- bind_rows(true_distances)
readr::write_csv(true_distances_df, 'results/multi_city/whw_matrices/distances.csv')
```
